SAT Competition 2020\tnoteref{title}

### 2021-06-08 paper/main.tex
..

From what was once mainly the archetypal intractable (in particular NP-complete) problem, propositional satisfiability 
(or Boolean satisfiability, SAT) has flourished into a success story of modern computer science~\cite{DBLP:series/faia/2009-185}.
This is due to advances in SAT solvers, i.e., implementations of decision procedures for SAT, which today form a 
central computational tool for solving real-world problem instances of various kinds of NP-hard search and optimization problems.
With standardized input formats, readily-available APIs for incremental applications,
and certified proof logging and checking capabilities, applications of SAT solver technology
have branched from the first breakthrough applications in automated planning, test pattern generation and hardware verification
to thousands of different application settings.

The success of SAT would not be possible without the persistent efforts of the SAT community to further improve the performance and robustness
of SAT solvers. The SAT Competition series, with a history dating back to early 90s, aims to support and provide further incentives 
for maintaining this progress. Organized yearly as an international open event, the SAT competitions (and their variants
in the forms of SAT Races and a SAT Challenge)~\cite{DBLP:journals/amai/SimonBH05,DBLP:conf/sat/BerreS03,DBLP:conf/sat/BerreS04,DBLP:journals/aim/JarvisaloBRS12,DBLP:journals/ai/BalintBJS15,DBLP:conf/aaai/BalyoHJ17,DBLP:journals/jsat/HeuleJS19}
 have a consistent track record in receiving tens of solver submissions yearly, submitted
by the community at large for obtaining a snapshot of the current state-of-the-art in practical SAT solving. Alongside participating solvers,
the competition invites through open calls submissions of benchmark instances representing, in particular, new interesting applications 
scenarios of SAT solvers. Indeed, in addition to evaluating recently developed solvers, an important aspect of the SAT competition series is
to collect on a yearly basis new benchmark sets, consisting of instances from various different application settings, which together with benchmark sets from previous years constitute a standard dataset for use in research papers and SAT solver development.

@@

We evaluated all 64 submitted solver configurations of which eight have been explicitly submitted to the No-Limits track, and four configurations were demoted to the No-Limits track due to wrong certificates. 
A total of six configurations got disqualified due to wrong answers. 
This left us with 46 configurations of 22 solvers inluding one Glucose hack.

@@

In the Incremental Library track we mimic scenarios
where a SAT solver is used as a back-end solver in a more complex tool
(typically solving a harder problem than SAT) and is called multiple times before 
the enclosing tool reaches its final state. 
``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}. 
Examples for applications of incremental SAT solving are Counter-Example Guided Abstraction Refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based Planning~\cite{Balyo:2017:IncrPlanning} or SAT Modulo Theories (SMT) solvers~\cite{Brummayer:2009:Boolector}.

Instead of using or extending the DIMACS input format, we realize the Incremental Library track
by relying on the general incremental interface IPASIR (Re-entrant Incremental Solver API) 
for SAT applications~\cite{Balyo:2015:SATRace}. The idea is that we actually run the 
enclosing tool on its own benchmark and communicate with the competing SAT solver 
through this interface API. 
%
Not only does the SAT solver in this track
need to solve a sequence of related problems fast, but its answers to the early questions
may, in general, influence which questions will follow next.
% E.g. Smaller unsat cores may allow the enclosing tool to converge using fewer SAT calls!

In this competition, two of the six submissions got disqualified, such that we had only four solvers competing in the Incremental track.

@@

The Parallel track evaluates the runtime performance in wall-clock time of SAT solvers making use of multiple processor cores.
The benchmarks %and the timeout (5000 seconds) 
are the same as in the Main track. 
%\textcolor{red}{repetitive? also mentioned below?}. 
%Each solver in this track was run on a m4.16xlarge machine from Amazon Web Services (AWS).
%These machines have 64 virtual cores and 256GB of memory. 
However, in contrast to the Main track, proof logging for unsatisfiable instances is not required in the Parallel track.

In the Parallel track, we evaluated ten solvers (in 14 configurations) out of which three solvers got disqualified due to wrong answers.

@@

New this year was the Cloud track, dedicated to evaluating distributed solvers running on multiple machines in a network. 
%\textcolor{red}{Not sure if terms ``distributed'' vs ``parallel'' are clear, could be more explicitly explained?}. 
%Similar to the Parallel track, the solvers ran on the Amazon cloud, but using 100 machines of the type m4.4xlarge, which have 16 virtual cores and 64GB of memory. 
Communication between the machines is possible using MPI and SSH.
%The wall-clock timeout is 1000 seconds and the same benchmarks were used as in the Main and Parallel track. \textcolor{red}{repetitive? also mentioned below?}
We evaluated six solvers in this track.

@@

The following requirements were imposed for 
participating in the competition.

@@

\paragraph{Description}
A short system description was required for each solver submission,
including a list of all the solver's authors and explaining any non-standard algorithmic
techniques and data structures, as well as references to the relevant literature.
These system descriptions have been collected and published in the competition
proceedings \cite{SC2020}.

\paragraph{Benchmarks}
To participate in the Main track, each team had to submit 20 new benchmark instances.
This rule guaranteed that the competition could be run on instances mostly unseen to the solver
developers prior to the competition. Moreover, by making these benchmarks publicly available
after the competition, the SAT community benefits by having an ever growing repository 
of diverse problems to target with the next developments.

The exact details of this rule are further explained in Section~\ref{sec:byob}.
Also the descriptions of the benchmarks have been published \cite{SC2020}.

@@

The benchmark instances were presented to the solvers in the de facto standard
DIMACS input format for propositional formulas in conjunctive normal form.
A simple extension of this format was to be adhered to when printing 
the satisfying assignment 
(see, e.g., \cite{DBLP:journals/jsat/HeuleJS19}, Section 2.4).

Proofs of unsatisfiability were to be emitted in the DRAT format~\cite{DRATtrim},
either in its textual version, which is also very similar to the DIMACS input format,
or in a more compact binary version (for more details, see \cite{satComp2020www}, Unsat Certificates).
%
Details on certification are further discussed in Section~\ref{sec:certif}.

@@

Each participant was allowed to be an author of at most four different sequential solvers,
two different parallel solvers, and one ``Glucose hack'' sub-track solver.
Two solvers were considered different as soon as their sources differed
or the compilation options were different, or different command line options were used
(with the exception of an option enabling or disabling the proof output).

@@

Apart from the No-limits track, participants were not allowed to submit a portfolio of solvers,
i.e., a combination of two or more core SAT solvers developed by different groups of authors.\footnote{In other words, a submission of a combination of solvers was only possible if all the authors of all the parts
were explicitly listed. This means that all the authors had to be notified if such participation
was planned and had to consider it carefully, also taking into account the limited number of submissions per author
as specified by the previous rule.}

This rule is mainly meant to encourage the SAT community to invest more effort into developing new solver code bases.
Moreover, while we acknowledge that research on solver selection tools that typically orchestrate portfolio solvers 
is interesting, it is not the focus of the SAT competition.

@@

Solvers were ranked using a PAR-2 score based on a \num{5000}-second timeout.
A PAR-2 system assigns as many points as the amount of time (in seconds) it took the solver
to solve a particular instance and twice the time limit, i.e.~\num{10000} points,
if the instance was not solved. This means that lowers scores are better.
We generally report the \emph{average score} of each solver across a benchmark set.

A SAT solver was disqualified if it produced a wrong answer. 
Specifically, if a solver reported ``unsatisfiable'' on an instance that 
was proven to be satisfiable by some other solver, or reported ``satisfiable'' 
but provided a wrong certificate. Solvers disqualified from the competition were
not eligible to win any award.

@@

In all tracks solvers were required to output a model to certify recognizing a satisfiable instance.
On the other hand, 
certificates for unsatisfiable instances (proofs) were required only 
in the Main track (besides the No Limits track).
In some cases, a solver output the correct result, but the respective certificate was wrong. 
Such solvers were demoted to the No-limits track of the competition.

The proofs were validated in a two-step fashion. First, the tool {\tt DRAT-trim}~\cite{DRATtrim}
was used for initial checking and optimizing the emitted proof, deriving a so-called LRAT proof file.
Afterwards, an independent, formally-verified checker {\tt cake\_lpr} \cite{cakeLprGithub}, 
was used for validating the LRAT proof as a correct proof of unsatisfiability of the given formula.
In the Main track, we only considered solved those unsatisfiable formulas that 
could be validated by {\tt DRAT-trim}.
There were several cases where {\tt cake\_lpr} ran out of resources before being able to 
confirm after {\tt DRAT-trim}. However, there was no case where {\tt DRAT-trim} would accept
a proof and {\tt cake\_lpr} would later disagree with the verdict.

@@

\label{sec:computing}
The Main, No-Limits, and Planning tracks were run on the StarExec cluster \cite{starexec}
with computing nodes  equipped with Intel Xeon \SI{2.4}{\giga\hertz} processors 
and \SI{128}{\giga\byte} of memory.
The time limit enforced on each solver for solving an instance was \SI{5000}{\second}. 
(In the Main track, validation then continued for up to \SI{45000}{\second}.)
The solvers were allowed to use the full \SI{128}{\giga\byte} of RAM.\footnote{
Unfortunately, the memory limit of \SI{24}{\giga\byte}, that was used in the previous years,
was by mistake advertised on the competition web page prior to solver submission.
This could have resulted in some solvers not ``daring'' to use the full \SI{128}{\giga\byte}
in the competition.}
The Incremental Library Track was run on computers with 2x Intel Xeon E5430 \SI{2.66}{\giga\hertz}
(4-Core) processors and \SI{24}{\giga\byte} of RAM.

%As noted above, 
The Parallel track was run on AWS m4.16xlarge machines with 64 virtual CPUs and 256 GB
of memory, while the Cloud track was run on AWS m4.4xlarge machines with 16 virtual CPUs and 64 GB of
memory. These tracks used wall-clock timeouts of \SI{5000}{\second} and \SI{1000}{\second}, respectively.

>>>>

From what was once mainly the archetypal intractable (in particular NP-complete) problem, propositional satisfiability 
(or Boolean satisfiability, SAT) has flourished into a success story of modern computer science~\cite{DBLP:series/faia/2009-185}.
This is due to advances in SAT solvers, i.e., implementations of decision procedures for SAT, which today form a 
central computational tool for solving real-world problem instances of various kinds of NP-hard search and optimization problems.
With standardized input formats, readily-available APIs for incremental applications,
and certified proof logging and checking capabilities, applications of SAT solver technology
have branched from the first breakthrough applications in automated planning, test pattern generation and hardware verification
to thousands of different application settings. \textcolor{red}{Add various references to the several things in this sentence}

The success of SAT would not be possible without the persistent efforts of the SAT community to further improve the performance and robustness
of SAT solvers. The SAT Competition series, with a history dating back to early 90s, aims to support and provide further incentives 
for maintaining this progress. Organized yearly as an international open event, SAT Competitions (and their variants
in the forms of SAT Races and a SAT Challenge)~\cite{DBLP:journals/amai/SimonBH05,DBLP:conf/sat/BerreS03,DBLP:conf/sat/BerreS04,DBLP:journals/aim/JarvisaloBRS12,DBLP:journals/ai/BalintBJS15,DBLP:conf/aaai/BalyoHJ17,DBLP:journals/jsat/HeuleJS19}
 have a consistent track record in receiving tens of solver submissions yearly, submitted
by the community at large for obtaining a snapshot of the current state-of-the-art in practical SAT solving. Alongside participating solvers,
the competition invites through open calls submissions of benchmark instances representing, in particular, new interesting applications 
scenarios of SAT solvers. Indeed, in addition to evaluating recently developed solvers, an important aspect of the SAT competition series is
to collect on a yearly basis new benchmark sets, consisting of instances from various different application settings, which together with benchmark sets from previous years constitute a standard dataset for use in research papers and SAT solver development.

@@

We evaluated all 64 solver submissions (including different configurations of specific solvers) 
to the Main track. Out of the 64 solvers, eight were explicitly submitted to the No-Limits track. Four solvers
 were demoted to the No-Limits track due to outputting invalid unsatisfiability proof certificates. 
Six solvers were disqualified due to outputting truth assignments which did not satisfy the corresponding benchmark instance.
This left us with 46 configurations of 22 solvers, inluding only one Glucose hack.

@@

In the Incremental Library track the underlying idea is to mimic scenarios
where a SAT solver is used as a back-end solver in a more complex tool
(typically solving a harder problem than SAT) and is called multiple times before 
the enclosing tool reaches its final state. 
``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.\textcolor{red}{Should we not cite the 2004 temporal induction paper by Niklases here?}
Examples for applications of incremental SAT solving are counterexample-guided eastraction refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based planning~\cite{Balyo:2017:IncrPlanning} and satisfiability modulo theories (SMT) solvers~\cite{Brummayer:2009:Boolector}.

Instead of using or extending the DIMACS input format, in the the Incremental Library track
a general incremental interface called IPASIR (Re-entrant Incremental Solver API) 
is employed~\cite{Balyo:2015:SATRace}. The idea is that we actually run the 
enclosing tool on its own benchmark and communicate with the competing SAT solver 
through this interface API. 
%
SAT solvers submitted to this track need hence implement the require interface.
Furthermore, it should be noted that the solutions output by a solver may, in general, influence
the fortchoming invocations of the solver.
% E.g. Smaller unsat cores may allow the enclosing tool to converge using fewer SAT calls!

Six solver were submitted to the Incremental Library track.
Two of the six solvers were disqualified due to outputting wrong answers.

@@

The Parallel track evaluates the runtime performance of SAT solvers making use of multiple processor cores
in terms of wall-clock time.
The benchmarks %and the timeout (5000 seconds) 
are the same as in the Main track. 
%\textcolor{red}{repetitive? also mentioned below?}. 
%Each solver in this track was run on a m4.16xlarge machine from Amazon Web Services (AWS).
%These machines have 64 virtual cores and 256GB of memory. 
In contrast to the Main track, proof logging for unsatisfiable instances is not required in the Parallel track.

A total of 14 solver configurations, based on 10 solvers, were submitted to the Parallel track.
Three solver configurations were disqualified due to wrong answers.

@@

The Cloud track was a new development in the SAT Competitions for 2020.
The track focuses on  evaluating distributed solvers running on multiple machines in a network. 
%\textcolor{red}{Not sure if terms ``distributed'' vs ``parallel'' are clear, could be more explicitly explained?}. 
%Similar to the Parallel track, the solvers ran on the Amazon cloud, but using 100 machines of the type m4.4xlarge, which have 16 virtual cores and 64GB of memory. 
Communication between the machines is possible using MPI and SSH.
%The wall-clock timeout is 1000 seconds and the same benchmarks were used as in the Main and Parallel track. \textcolor{red}{repetitive? also mentioned below?}
We received six solver submissions to the Cloud track.

@@

The following requirements were imposed for 
participating in SAT Competition 2020.

@@

\paragraph{Description}
A short system description was required for each solver submission,
including a list of all  authors involved in developing the solver,  description of any non-standard algorithmic
techniques and data structures implemented in the sovler, as well as references to the relevant literature.
These system descriptions have been collected and made available publically in the non-refereed competition
proceedings~\cite{SC2020}.

\paragraph{Benchmarks}
The authors of solvers participating in the Main track were required 
  to submit 20 ``new'' benchmark instances.
The exact details of this rule are further explained in Section~\ref{sec:byob}.
In short, this rule guaranteed that the competition could be run on instances mostly unseen to the solver
developers prior to the competition. Moreover, by making these benchmarks publicly available
after the competition, the SAT community benefits by having an ever growing repository 
of diverse problems to target with the next developments.
The descriptions of the submitted benchmarks are also made available in the competition proceedings~\cite{SC2020}.

@@

The benchmark instances were presented to the solvers in the de facto standard
DIMACS input format for propositional formulas in conjunctive normal form (CNF).
A simple extension of this format was to be adhered to when printing 
the satisfying assignment 
(see, e.g., \cite{DBLP:journals/jsat/HeuleJS19}, Section 2.4).

Where required, proofs of unsatisfiability were to be output in the DRAT format~\cite{DRATtrim},
either in its textual version---which is also very similar to the DIMACS input format---or 
in a more compact binary version (for more details, see \cite{satComp2020www}, Unsat Certificates).
%
Details on certification are further discussed in Section~\ref{sec:certif}.

@@

Due to the shear number of participants in the SAT Competitions, in order to make it
feasible to run the whole competition, specific limits were set on the number of submitted solvers.
In particular, each solver author was allowed to be an author of at most four different sequential solvers,
two different parallel solvers, and one ``Glucose hack'' sub-track solver.
Two solvers were considered different as soon as their sources differed
or the compilation options were different, or different command line options were used
(with the exception of an option enabling or disabling the proof output).

@@

Apart from the No-limits track, participants were not allowed to submit a portfolio of solvers,
i.e., a combination of two or more core SAT solvers developed by different groups of authors.\footnote{In other words, a submission of a combination of solvers was only possible if all the authors of all the parts
were explicitly listed. This means that all the authors had to be notified if such participation
was planned and had to consider it carefully, also taking into account the limited number of submissions per author
as specified by the previous rule.}
This rule is mainly meant to encourage the SAT community to invest more effort into developing new solver code bases.
Moreover, while we acknowledge that research on solver selection tools that typically orchestrate portfolio solvers 
is interesting, it is not at present the focus of the SAT competitions.

@@

Solvers were ranked using a PAR-2 score based on a \num{5000}-second timeout.
A PAR-2 system assigns as many points as the amount of time (in seconds) it took the solver
to solve a particular instance and twice the time limit, i.e.~\num{10000} points,
if the instance was not solved. In particular, this mean that the lower the score a solver
obtained, the better the solver performs.
%We generally report the \emph{average score} of each solver across a benchmark set.

A  solver was disqualified if it produced a wrong answer:
specifically, if a solver reported ``unsatisfiable'' on an instance that 
was proven to be satisfiable by some other solver, or reported ``satisfiable'' 
but provided a wrong certificate. Solvers disqualified from the competition were
not eligible for awards.

@@

In all tracks solvers were required to output a solution (a satisfying truth assignment, i.e., a model on the instance in question)
 to certify recognizing a satisfiable instance.
On the other hand, 
certificates for unsatisfiable instances (proofs) were required only 
in the Main track (besides the No-Limits track).
In some cases, a solver output the correct result, but the respective certificate was wrong. 
Such solvers were demoted to the No-Limits track of the competition.

The proofs were validated in a two-step fashion. First, the tool {\tt DRAT-trim}~\cite{DRATtrim}
was used for initial checking and optimizing the emitted proof, deriving a so-called LRAT proof file.
Afterwards, an independent formally-verified checker {\tt cake\_lpr} \cite{cakeLprGithub}
was used for validating the LRAT proof as a correct proof of unsatisfiability of the given formula.
In the Main track, only those unsatisfiable benchmark instances for which the proof emitted by a specific solver
could be validated by {\tt DRAT-trim} were considered solved by the  solver.
It should be noted that, while there were several cases where {\tt cake\_lpr} ran out of resources before 
there was no case where {\tt DRAT-trim} would accept
a proof and {\tt cake\_lpr} would later disagree with the verdict.
\textcolor{red}{This is pretty vague... does not really say if there were proofs that could not be validated with DRAT-trim??}

@@

\label{sec:computing}
The Main, No-Limits, and Planning tracks were run on the StarExec cluster \cite{starexec}
with computing nodes  equipped with Intel Xeon \SI{2.4}{\giga\hertz} processors 
and \SI{128}{\giga\byte} of memory.
The time limit enforced on each solver for solving an instance was \SI{5000}{\second}. 
In the Main track, proof validation was limited to \SI{45000}{\second} per proof.)
The solvers were allowed to use the full \SI{128}{\giga\byte} of RAM.\footnote{
Unfortunately, the memory limit of \SI{24}{\giga\byte}, that was used in the previous years,
was by mistake advertised on the competition web page prior to solver submission.
This could have resulted in some solvers not ``daring'' to use the full \SI{128}{\giga\byte}
in the competition. We do not, however, have concrete evidence to support this possibility.}

The Incremental Library Track was run on computers with 2x Intel Xeon E5430 \SI{2.66}{\giga\hertz}
(4-Core) processors and \SI{24}{\giga\byte} of RAM.
The Parallel track was run on AWS m4.16xlarge machines with 64 virtual CPUs and 256 GB
of memory, while the Cloud track was run on AWS\textcolor{red}{Was AWS spelled out a single time before this? I now notice that
we do not really mention Amazon much, should we mention it more specifically?}
 m4.4xlarge machines with 16 virtual CPUs and 64 GB of
memory. These tracks used wall-clock timeouts of \SI{5000}{\second} and \SI{1000}{\second}, respectively.
